Computing Entropies With Nested Sampling

### 2017-03-20 paper/ms.tex
Jared

\acknowledgments{Acknowledgements}
It is a pleasure to thank the following people for interesting and helpful
conversations about this topic: Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), David Hogg (NYU), Kevin Knuth (SUNY Albany),
Iain Murray (Edinburgh). This work was supported by Centre for eResearch
at the University of Auckland.

@@

\authorcontributions{Author Contributions}

%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\acknowledgments{Acknowledgements}
It is a pleasure to thank the following people for interesting and helpful
conversations about this topic: Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), David Hogg (NYU), Kevin Knuth (SUNY Albany),
Iain Murray (Edinburgh), Jared Tobin (jtobin.io).
This work was supported by Centre for eResearch
at the University of Auckland.

@@

%\authorcontributions{Author Contributions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
